EoS-insensitive relations after GW170817

### 2019-01-20 paper/bin-love-after-gw170817.tex
comment on radius

In addition, Fig.~\ref{fig:rlove} displays the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
Similar to the fits performed for the I-Love-Q and C-Love relations, we fit the R-Love relations to Eq.~\ref{eq:ILQfitNew} with a Newtonian control factor the same as used in the C-Love case seen in Eq.~\ref{eq:cloveFit}, where the NS mass is substituted with the polytropic form $M\propto R^{(3-n)/(1-n)}$~\cite{Shapiro:MRpolytrope}.
Noting that most physical EoSs obey approximate polytropic indices between $0.50$ and $1.00$, as shown in Ref.~\cite{Yagi:binLove}, we choose a central value of $n=0.75$ for use in this analysis, resulting in $M\propto R^9$.
Absorbing the proportionality constant into $K_{R\Lambda}$ gives the approximate Newtonian relationship as:
\begin{equation}
R^N \approx K_{R\Lambda}\Lambda^{-1/40}.
\end{equation}
The results of this fit are displayed in Tab.~\ref{tab:ILQfitNew}, and the maximal EoS variability is again shown in Tab.~\ref{tab:maxVar}.
As can be seen with the unconstrained EoSs, previously this relation was not very universal, and gave large uncertainties ($\sim50\%$) on the mapping from tidal deformability to radius.
Now, however, upon the restriction to soft EoSs conforming to GW170817 observe a large decrease in EoS variability to $\sim20\%$, making these relations EoS insensitive to some degree (on the same scale as the binary Love relations).
\begin{figure}
\begin{center} 
\includegraphics[width=1\columnwidth]{RL.eps}
\end{center}
\caption{
Similar to Fig.~\ref{fig:clove} but for the R-Love relationships between the NS radius and tidal deformability.
In this figure, we also construct fits to  Eq.~\ref{eq:ILQfitNew}, limiting to the Newtonian case $\bar{R} \sim M\Lambda^{1/5}$, with $M\sim R^{(3-n)/(1-n)}$ for polytropic index $n$.
Observe how the fractional difference from the fit is reduced significantly between the unconstrained and constrained sets of EoSs, shown by the comparisons in Tab.~\ref{tab:maxVar}.
Also shown in this figure is the hybrid star R-Love relations along with their fractional difference from the constrained EoS fits (dashed green).
}
\label{fig:rlove}
\end{figure}

>>>>

\kc{The R-Love fit is not a new relation, it is the same as C-Love. So instead of refitting you should just reexpress the C(Love) fit as R=m/C(Love). The errors you are finding here are way larger than error I've been finding from simply using C(Love) to compute the radius, and this might be the reason.}
In addition, Fig.~\ref{fig:rlove} displays the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
Similar to the fits performed for the I-Love-Q and C-Love relations, we fit the R-Love relations to Eq.~\ref{eq:ILQfitNew} with a Newtonian control factor the same as used in the C-Love case seen in Eq.~\ref{eq:cloveFit}, where the NS mass is substituted with the polytropic form $M\propto R^{(3-n)/(1-n)}$~\cite{Shapiro:MRpolytrope}.
Noting that most physical EoSs obey approximate polytropic indices between $0.50$ and $1.00$, as shown in Ref.~\cite{Yagi:binLove}, we choose a central value of $n=0.75$ for use in this analysis, resulting in $M\propto R^9$.
Absorbing the proportionality constant into $K_{R\Lambda}$ gives the approximate Newtonian relationship as:
\begin{equation}
R^N \approx K_{R\Lambda}\Lambda^{-1/40}.
\end{equation}
The results of this fit are displayed in Tab.~\ref{tab:ILQfitNew}, and the maximal EoS variability is again shown in Tab.~\ref{tab:maxVar}.
As can be seen with the unconstrained EoSs, previously this relation was not very universal, and gave large uncertainties ($\sim50\%$) on the mapping from tidal deformability to radius.
Now, however, upon the restriction to soft EoSs conforming to GW170817 observe a large decrease in EoS variability to $\sim20\%$, making these relations EoS insensitive to some degree (on the same scale as the binary Love relations).
\begin{figure}
\begin{center} 
\includegraphics[width=1\columnwidth]{RL.eps}
\end{center}
\caption{
Similar to Fig.~\ref{fig:clove} but for the R-Love relationships between the NS radius and tidal deformability.
In this figure, we also construct fits to  Eq.~\ref{eq:ILQfitNew}, limiting to the Newtonian case $\bar{R} \sim M\Lambda^{1/5}$, with $M\sim R^{(3-n)/(1-n)}$ for polytropic index $n$.
Observe how the fractional difference from the fit is reduced significantly between the unconstrained and constrained sets of EoSs, shown by the comparisons in Tab.~\ref{tab:maxVar}.
Also shown in this figure is the hybrid star R-Love relations along with their fractional difference from the constrained EoS fits (dashed green). \kc{The radius needs to be in km in both panels (not fractional error).}
}
\label{fig:rlove}
\end{figure}
